---
title: "practiceactivity_ibrayeva"
author: "sofiya"
date: "2024-02-08"
output: html_document
---

***Sofiya Ibrayeva***

# Purpose of the assignment

The purpose of this assignment is to engage with the R software.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Create a new variable 'b' with value 1947.01 and check the class of 'b'

```{r}
b <- 1947.01
class(b)
```

```{r}
class_b <- class(b)
print(paste("Class of b:", class_b))
```

## 2. Convert 'b' from previous exercise to character and store the result into a new variable 'b_char'

```{r}
b_char <- "1947.01"
class_b_char <- class(b_char)
print(paste("Class of b_char:", class_b_char))
```

## 3. Create a vector containing following mixed elements {1, 'a', 2, 'b'} and find out its class

```{r}
vector1 <- c(1, 'a', 2, 'b')
class_vector1 <- class(vector1)
print(paste("Class of vector1:", class_vector1))
```

## 4. Create a dataframe and name it DF. This dataframe should contain Three columns with the following names C1, C2 and C3. C1 should contain numeric values 1 and 4.37. C2 should contain "Red" and "Blue" and C3 should contain TRUE and FALSE

```{r}
df1 <- data.frame(C1=c(1, 4.37), C2=c('Red', 'Blue'), C3=c(T, F))
print(df1)
```

## 5. Select and print C1 column of the DF dataframe in the previous example

```{r}
df1$C1
df1$C2
```

```{r}
summary_df1 <- summary(df1)
print("Summary statistics of df1:")
print(summary_df1)
```

```{r}
subset_df1 <- subset(df1, C1 > 2)
print("Subset of df1 where C1 > 2:")
print(subset_df1)
```

## 6. Show the frequency (i.e. count) of each of the countries in the data frame.

```{r}
df2 <- data.frame(V1=1:6, Countries=c('US', 'UK', 'UK', 'India', 'China', 'India'))
df2
```

```{r}
table(df2$Countries)
```

## 7. Define a variable x=0.75. write a code to crat a variable y whose value is dependent on the value of x. If x is positive, y should be set to 14 otherwise it should be set -19.7. Change the value of x to -1 and evaluate your code again.

```{r}
x <- 0.75
if (x>0){y=14}else{
y=-19.7}
print(x)
print(y)
```

```{r}
x <--1
if (x>0){y=14}else{
y=-19.7}
print(x)
print(y)
```
